Adopting the Euro: a Synthetic Control Approach \\ Online Appendix\\ \vspace{2em}

### 2024-01-30 Text/Manuscript.tex

Share of Priv. Consumption &     56.27 &     54.55 \\  
Share of Investment &     26.53 &     26.01 \\  

@@

Share of Imports &     32.57 &     35.91 \\  
Share of Exports &     31.85 &     33.86 \\  
Employment Share &     45.16 &     48.26 \\  
Labor productivity growth &      2.32 &      1.34 \\  

@@

Share of Priv. Consumption &     52.51 &     53.92 \\  
Share of Investment &     26.66 &     25.07 \\  
Share of Gov. Consumption &     19.38 &     20.13 \\  
Share of Imports &     26.57 &     27.70 \\  
Share of Exports &     28.02 &     26.81 \\  
Employment Share &     47.26 &     47.27 \\  
Labor productivity growth &      2.99 &      2.04 \\  

@@

Share of Priv. Consumption &     55.16 &     55.12 \\  
Share of Investment &     23.11 &     23.17 \\  
Share of Gov. Consumption &     21.24 &     20.67 \\  
Share of Imports &     20.54 &     24.60 \\  
Share of Exports &     21.03 &     23.56 \\  
Employment Share &     40.49 &     44.53 \\  
Labor productivity growth &      2.11 &      1.16 \\  
Inflation Rate &      6.22 &     11.96 \\   \hline

@@

Share of Priv. Consumption &     57.15 &     57.23 \\  
Share of Investment &     24.50 &     26.13 \\  
Share of Gov. Consumption &     19.68 &     14.94 \\  
Share of Imports &     21.40 &     36.07 \\  
Share of Exports &     20.06 &     34.36 \\  
Employment Share &     48.36 &     49.49 \\  
Labor productivity growth &      2.35 &      0.95 \\  
Inflation Rate &      3.54 &      4.47 \\  \hline

@@

Share of Priv. Consumption &     63.06 &     62.56 \\  
Share of Investment &     26.46 &     22.24 \\  
Share of Gov. Consumption &     16.75 &     15.84 \\  
Share of Imports &     21.77 &     22.24 \\  
Share of Exports &     15.50 &     22.87 \\  
Employment Share &     38.77 &     41.69 \\  
Labor productivity growth &      1.44 &      1.09 \\  
Inflation Rate &     14.70 &     14.71 \\    \hline

@@

Share of Priv. Consumption &     61.17 &     55.50 \\  
Share of Investment &     21.65 &     24.24 \\  
Share of Gov. Consumption &     18.72 &     24.34 \\  
Share of Imports &     52.85 &     30.59 \\  
Share of Exports &     51.30 &     34.67 \\  
Employment Share &     35.36 &     39.90 \\  
Labor productivity growth &      3.44 &      2.02 \\  
Inflation Rate &      8.36 &     47.41 \\   \hline

@@

Share of Priv. Consumption &     59.00 &     57.32 \\  
Share of Investment &     22.87 &     23.15 \\  
Share of Gov. Consumption &     17.55 &     18.87 \\  
Share of Imports &     19.28 &     19.88 \\  
Share of Exports &     19.86 &     19.22 \\  
Employment Share &     38.25 &     44.13 \\  
Labor productivity growth &      2.16 &      1.23 \\  
Inflation Rate &      9.48 &     12.94 \\  \hline

@@

Share of Priv. Consumption &     48.16 &     55.38 \\  
Share of Investment &     22.57 &     26.28 \\  
Share of Gov. Consumption &     15.33 &     22.74 \\  
Share of Imports &     81.83 &     35.72 \\  
Share of Exports &     95.78 &     40.11 \\  
Employment Share &     46.63 &     45.79 \\  
Labor productivity growth &      1.91 &      1.41 \\  
Inflation Rate &      4.61 &     35.04 \\  \hline

@@

Share of Priv. Consumption &     50.90 &     54.79 \\  
Share of Investment &     22.62 &     26.17 \\  
Share of Gov. Consumption &     21.94 &     18.39 \\  
Share of Imports &     47.47 &     38.28 \\  

@@

Share of Priv. Consumption &     66.93 &     65.47 \\  
Share of Investment &     26.93 &     21.34 \\  
Share of Gov. Consumption &     14.03 &     13.93 \\  
Share of Imports &     31.16 &     21.09 \\  
Share of Exports &     23.27 &     21.83 \\  
Employment Share &     41.81 &     38.56 \\  
Labor productivity growth &      1.95 &      1.24 \\  
Inflation Rate &     14.14 &     19.60 \\   \hline

@@

Share of Priv. Consumption &     63.12 &     63.00 \\  
Share of Investment &     23.78 &     22.13 \\  
Share of Gov. Consumption &     14.51 &     15.26 \\  
Share of Imports &     18.55 &     17.59 \\  
Share of Exports &     17.13 &     17.97 \\  
Employment Share &     35.38 &     42.17 \\  
Labor productivity growth &      2.55 &      1.07 \\  
Inflation Rate &      9.87 &     14.12 \\  \hline

@@

\begin{landscape}
\begin{table}[htbp]
\scriptsize
\caption{\label{TA_weights_placebo}  Composition of the Doppelgangers: Country Weights (in \%)}\centering\medskip
\begin{tabular}{lcccccccccccc} \toprule
\textit{Donor countries} & Austria  & Belgium  & Finland  & France  & Germany  & Greece  & Ireland  & Italy  & Luxembourg  & Netherlands  & Portugal  & Spain  \\  \midrule
Australia &      18.1 &       $<0.1$ &      39.6 &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       0.1 \\  
Canada &       $<0.1$ &       $<0.1$ &      22.6 &      52.0 &      18.3 &       $<0.1$ &       $<0.1$ &      32.4 &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ \\  
Chile &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &      22.0 &       $<0.1$ &       5.2 &       $<0.1$ &       $<0.1$ &       $<0.1$ \\  
Iceland &       $<0.1$ &       $<0.1$ &      17.2 &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ \\  
Israel &      16.4 &      24.6 &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &      50.1 &       $<0.1$ &      52.3 &      12.0 &      15.1 &       4.0 \\  
Korea &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       1.9 &       $<0.1$ \\  
Mexico &       1.8 &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &      39.8 &      17.5 \\  
New Zealand &      18.6 &       $<0.1$ &       $<0.1$ &      32.9 &      10.4 &      30.8 &       $<0.1$ &       4.1 &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ \\  
Norway &      13.3 &       $<0.1$ &       $<0.1$ &      15.1 &       $<0.1$ &       $<0.1$ &      27.9 &       $<0.1$ &       $<0.1$ &      22.6 &       $<0.1$ &       $<0.1$ \\  
Switzerland &      31.8 &      75.4 &      20.6 &       $<0.1$ &      35.6 &       2.6 &       $<0.1$ &      12.2 &      42.5 &      65.4 &      26.7 &      21.3 \\  
United States &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &      35.7 &      66.6 &       $<0.1$ &      51.3 &       $<0.1$ &       $<0.1$ &      16.6 &      57.1 \\
\bottomrule
\end{tabular}
\annote{This table summarizes the weights in percent attributed to each donor country to construct the synthetic treated units. Relative to the baseline analysis, the donor pool now excludes Denmark, Sweden and the United Kingdom.}
\end{table}

>>>>

Share of Priv. Consumption &     56.27 &     54.58 \\  
Share of Investment &     26.53 &     26.02 \\  

@@

Share of Imports &     32.57 &     35.93 \\  
Share of Exports &     31.85 &     33.92 \\  
Employment Share &     45.16 &     48.31 \\  
Labor productivity growth &      2.32 &      1.35 \\  

@@

Share of Priv. Consumption &     52.51 &     50.11 \\  
Share of Investment &     26.66 &     26.39 \\  
Share of Gov. Consumption &     19.38 &     21.69 \\  
Share of Imports &     26.57 &     33.64 \\  
Share of Exports &     28.02 &     31.84 \\  
Employment Share &     47.26 &     48.27 \\  
Labor productivity growth &      2.99 &      2.16 \\  

@@

Share of Priv. Consumption &     55.16 &     55.17 \\  
Share of Investment &     23.11 &     23.08 \\  
Share of Gov. Consumption &     21.24 &     20.72 \\  
Share of Imports &     20.54 &     24.69 \\  
Share of Exports &     21.03 &     23.66 \\  
Employment Share &     40.49 &     44.51 \\  
Labor productivity growth &      2.11 &      1.15 \\  
Inflation Rate &      6.22 &     11.59 \\   \hline

@@

Share of Priv. Consumption &     57.15 &     58.33 \\  
Share of Investment &     24.50 &     25.60 \\  
Share of Gov. Consumption &     19.68 &     14.79 \\  
Share of Imports &     21.40 &     31.43 \\  
Share of Exports &     20.06 &     30.15 \\  
Employment Share &     48.36 &     49.07 \\  
Labor productivity growth &      2.35 &      1.03 \\  
Inflation Rate &      3.54 &      4.54 \\  \hline

@@

Share of Priv. Consumption &     63.06 &     62.61 \\  
Share of Investment &     26.46 &     22.01 \\  
Share of Gov. Consumption &     16.75 &     15.77 \\  
Share of Imports &     21.77 &     23.49 \\  
Share of Exports &     15.50 &     23.87 \\  
Employment Share &     38.77 &     41.82 \\  
Labor productivity growth &      1.44 &      0.97 \\  
Inflation Rate &     14.70 &     15.28 \\    \hline

@@

Share of Priv. Consumption &     61.17 &     55.84 \\  
Share of Investment &     21.65 &     25.10 \\  
Share of Gov. Consumption &     18.72 &     19.06 \\  
Share of Imports &     52.85 &     32.05 \\  
Share of Exports &     51.30 &     32.05 \\  
Employment Share &     35.36 &     40.78 \\  
Labor productivity growth &      3.44 &      2.28 \\  
Inflation Rate &      8.36 &     33.46 \\   \hline

@@

Share of Priv. Consumption &     59.00 &     62.10 \\  
Share of Investment &     22.87 &     22.38 \\  
Share of Gov. Consumption &     17.55 &     16.95 \\  
Share of Imports &     19.28 &     19.64 \\  
Share of Exports &     19.86 &     21.07 \\  
Employment Share &     38.25 &     42.35 \\  
Labor productivity growth &      2.16 &      1.56 \\  
Inflation Rate &      9.48 &     11.20 \\  \hline

@@

Share of Priv. Consumption &     48.16 &     57.18 \\  
Share of Investment &     22.57 &     28.27 \\  
Share of Gov. Consumption &     15.33 &     14.76 \\  
Share of Imports &     81.83 &     39.39 \\  
Share of Exports &     95.78 &     39.60 \\  
Employment Share &     46.63 &     49.28 \\  
Labor productivity growth &      1.91 &      1.42 \\  
Inflation Rate &      4.61 &     14.66 \\   \hline

@@

Share of Priv. Consumption &     50.90 &     54.78 \\  
Share of Investment &     22.62 &     26.16 \\  
Share of Gov. Consumption &     21.94 &     18.40 \\  
Share of Imports &     47.47 &     38.27 \\  

@@

Share of Priv. Consumption &     66.93 &     64.53 \\  
Share of Investment &     26.93 &     21.90 \\  
Share of Gov. Consumption &     14.03 &     15.06 \\  
Share of Imports &     31.16 &     22.84 \\  
Share of Exports &     23.27 &     24.34 \\  
Employment Share &     41.81 &     41.35 \\  
Labor productivity growth &      1.95 &      1.75 \\  
Inflation Rate &     14.14 &     14.12 \\   \hline

@@

Share of Priv. Consumption &     63.12 &     65.77 \\  
Share of Investment &     23.78 &     20.50 \\  
Share of Gov. Consumption &     14.51 &     15.36 \\  
Share of Imports &     18.55 &     20.84 \\  
Share of Exports &     17.13 &     22.47 \\  
Employment Share &     35.38 &     39.80 \\  
Labor productivity growth &      2.55 &      1.44 \\  
Inflation Rate &      9.87 &     16.90 \\  \hline

@@

\begin{landscape}
\begin{table}[htbp]
\scriptsize
\caption{\label{TA_weights_placebo}  Composition of the Doppelgangers: Country Weights (in \%)}\centering\medskip
\begin{tabular}{lcccccccccccc} \toprule
\textit{Donor countries} & Austria  & Belgium  & Finland  & France  & Germany  & Greece  & Ireland  & Italy  & Luxembourg  & Netherlands  & Portugal  & Spain  \\  \midrule
Australia &      $<0.1$ &       $<0.1$ &     $<0.1$ &       27.2 &       $<0.1$ &       $<0.1$ &       $<0.1$ &       13.4 &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ \\  
Canada &       $<0.1$ &       $<0.1$ &      67.7 &     37.4 &      23.0 &       12.8 &       $<0.1$ &      27.4 &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ \\  
Chile &       $<0.1$ &       $<0.1$ &       $<0.1$ &       0.1 &       $<0.1$ &      1.7 &      22.0 &       $<0.1$ &       5.2 &       $<0.1$ &       $<0.1$ &       $<0.1$ \\  
Iceland &       $<0.1$ &       $<0.1$ &      9.6 &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ \\  
Israel &     $<0.1$ &      $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &      50.1 &       $<0.1$ &      56.0 &      12.0 &      $<0.1$ &       $<0.1$ \\  
Korea &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       4.4 &       $<0.1$ \\  
Mexico &       23.2 &       $<0.1$ &       $<0.1$ &       $<0.1$ &       $<0.1$ &       19.6 &       $<0.1$ &      11.9 &       $<0.1$ &       $<0.1$ &      42.4 &      22.2 \\  
New Zealand &      7.5 &       $<0.1$ &       $<0.1$ &      19.8 &      $<0.1$ &    65.9 &       $<0.1$ &       39.7 &       $<0.1$ &       $<0.1$ &       $<0.1$ &       8.2 \\  
Norway &      25.3 &       41.9 &       $<0.1$ &      $<0.1$ &       $<0.1$ &       $<0.1$ &      27.9 &       $<0.1$ &       $<0.1$ &      22.6 &       $<0.1$ &       $<0.1$ \\  
Switzerland &      44.0 &      58.1 &      22.7 &       $<0.1$ &      43.1 &      $<0.1$ &       $<0.1$ &      $<0.1$ &      44.0 &      65.4 &     31.4 &      19.7 \\  
United States &       $<0.1$ &       $<0.1$ &       $<0.1$ &       15.5 &      33.9 &     $<0.1$ &       $<0.1$ &      7.6 &       $<0.1$ &       $<0.1$ &      21.8 &      49.9 \\
\bottomrule
\end{tabular}
\annote{This table summarizes the weights in percent attributed to each donor country to construct the synthetic treated units. Relative to the baseline analysis, the donor pool now excludes Denmark, Sweden and the United Kingdom.}
\end{table}
